Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-29 Paper/MSRChallenge2017.tex
adding stuff to related work

The most similar related work to this paper is a case study investigating how
social and technical factors affect build
success on a project with 40 developers~\cite{Hassan06}.
We focus on a wide range of open source projects and
measure experience through developer profile information.
Other work has investigated the effects of various factors, such as team
organization, on predicting build success in a single
project~\cite{Kwan11,Wolf09}.
Previous investigations have established relationships between both social and 
technical 
attributes and 
different measures of success, such as pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show the importance of the social connection between the developer initiating a
pull request and the project integrators. We look at a broader aspect of 
social factors, and focus on predicting the Travis CI build success.
Gousios et al.~\cite{gousios14} found that the commit change location is
an important indicator to commit acceptance rate, and that including
test cases increases a
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, while Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast with their work, we focus on the relationship between social 
attributes and continuous integration success.

>>>>

The most similar related work to this paper is a case study investigating how
social and technical factors affect build
success on a project with 40 developers~\cite{Hassan06}.
We focus on a wide range of open source projects and
measure experience through developer profile information.
Other work has investigated the effects of various factors, such as team
organization, on predicting build success in a single
project~\cite{Kwan11,Wolf09}.
Previous investigations have established relationships between both social and 
technical 
attributes and 
different measures of success, such as pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse} or evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show the importance of the social connection between the developer initiating a
pull request and the project integrators. We look at a broader aspect of 
social factors, and focus on predicting the Travis CI build success.
Gousios et al.~\cite{gousios14} found that the commit change location is
an important indicator to commit acceptance rate and that including
test cases increases a
commit's acceptance rate~\cite{gousios15}. We found that number of followers and being a core member are important indicators of built success. 
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, while Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. In our study we focus on the comparisson between similar technical characteristics and social attributes. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality, while we focus on gain in predictability of software quality when using CI.
